|

### 2017-10-07 manuscript.Rmd
Adds Dirk's suggestions:
1. Moves "portability" section below "interfaces" & "sandboxed"

2. Moves comment about singularity to later in that section and clarifies relevance. Drops shifter reference.

3. use footnote on download stats for tidyverse (& updates stats again)

One common use case for Rocker containers is to provide a fast and
reliable mechanism to deploy a custom R environment to a remote server, such
as Amazon Web Services Elastic Compute (AWS EC2), DigitalOcean, NSF's
Jetstream servers \citep{jetstream}, or private or institutional server hardware. 
Lawrence Berkeley National Labs (LBNL) has made `Singularity`: software which can import
and run Docker containers without root privileges, as most cluster administrators require \citep{singularity}. Another LBNL project, *Shifter*, allows Docker containers to be deployed on supercomputing
architectures such as CRAY \citep{shifter}.

Importantly, Rocker containers are just as easy to run locally on most modern laptops
by first installing the appropriate Docker command (or distribution) for Windows, MacOS, and Linux-based
operating systems. By sharing volumes with the local host, users can still manipulate
files with familiar, native tools while performing computation through a reproducible,
containerized environment \citep{Boettiger2015}. Being
able to test code in a predictable, pre-configured R environment on a
local machine and to then run the same code in an identical environment on a
remote server (e.g. for access to greater RAM, more processors, or merely
to free up the local machine from a long-running computation) is essential
for low-friction scaling of analysis.  Without such containerization,
getting code to run appropriately in a remote environment can be a major
undertaking, requiring both time and knowledge many would-be users may
not have.

@@

@@

image            | description                               | size   | downloads 
---------------- | ----------------------------------------- | ------ | ------- 
[r-ver](https://hub.docker.com/r/rocker/r-ver)          |  Version-stable base R & src build tools  | 219 MB | 2,000
[rstudio](https://hub.docker.com/r/rocker/rstudio)      |  Adds rstudio                             | 334 MB | 285,000
[tidyverse](https://hub.docker.com/r/rocker/tidyverse)  |  Adds tidyverse & devtools                | 656 MB | 14,000 (+46,000 as `hadleyverse`)
[verse](https://hub.docker.com/r/rocker/verse)          |  Adds java, tex & publishing-related packages   | 947 MB | 4,000
[geospatial](https://hub.docker.com/r/rocker/geospatial)|  Adds geospatial libraries   |  1.3 GB | 1,000

@@

<!-- DE The (+46,000 as hadleyverse) is visually very awkward. Can the "+46k" be a footnote? I know nothing about Markdown tables but would be happy to redo 1 + 2 in latex ...-->

>>>>

@@

One common use case for Rocker containers is to provide a fast and
reliable mechanism to deploy a custom R environment to a remote server, such
as Amazon Web Services Elastic Compute (AWS EC2), DigitalOcean, NSF's
Jetstream servers \citep{jetstream}, or private or institutional server hardware.
Rocker containers are  also easy to run locally on most modern laptops
by first installing the appropriate Docker command (or distribution) for Windows, MacOS, and Linux-based
operating systems. By sharing volumes with the local host, users can still manipulate
files with familiar, native tools while performing computation through a reproducible,
containerized environment \citep{Boettiger2015}. Being
able to test code in a predictable, pre-configured R environment on a
local machine and to then run the same code in an identical environment on a
remote server (e.g. for access to greater RAM, more processors, or merely
to free up the local machine from a long-running computation) is essential
for low-friction scaling of analysis.  Without such containerization,
getting code to run appropriately in a remote environment can be a major
undertaking, requiring both time and knowledge many would-be users may
not have.

Deploying Docker containers on centrally administrated multi-user machines, such
as department or university clusters, has previously been more difficult, since
system adminstrators do not want to allow the elevated user permissions the Docker
runtime enviornment requires.  To work around this problem, Lawrence Berkeley National
Labs (LBNL) has made `Singularity`: a container runtime environment that users can
both install and use to run most Docker containers without requiring root privileges\citep{singularity},
making it easier to deploy Rocker containers in this context as well.

@@

image            | description                               | size   | downloads 
---------------- | ----------------------------------------- | ------ | ------- 
[r-ver](https://hub.docker.com/r/rocker/r-ver)          |  Version-stable base R & src build tools  | 219 MB | 6,000
[rstudio](https://hub.docker.com/r/rocker/rstudio)      |  Adds rstudio                             | 334 MB | 314,000
[tidyverse](https://hub.docker.com/r/rocker/tidyverse)  |  Adds tidyverse & devtools                | 656 MB | 83,000 [^1]
[verse](https://hub.docker.com/r/rocker/verse)          |  Adds java, tex & publishing-related packages   | 947 MB | 9,000
[geospatial](https://hub.docker.com/r/rocker/geospatial)|  Adds geospatial libraries   |  1.3 GB | 4,000

@@

[^1]: Includes 49,000 under eariler name, `hadleyverse`.
